\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-11 WOOT/Files/badusb.tex
add some impl, minor fix

As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension. Based on this pattern, we summaries our implementation of \tool into the following parts and their comparison can be found in Table~\ref{table:mode_comparison}:
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Mode & Detectibility & Automation & Power Consumption  \\
	\hline
	Scripting & Medium & Yes & Low\\
	\hline
	Remote Control & High & No & High \\
	\hline
	Privacy Extraction & Low & Yes & Medium\\
	\hline
	\end{tabular}
	\linebreak
	\caption{Comparison of Different Mode}
	\label{table:mode_comparison}
\end{table*}
\begin{itemize}
	\item\textit{Hardware specification} the  hardware we uses to build \tool
	\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like GoodUSB\cite{tian2015defending}
	\shuqing{Cannot bypass USBCheckIn.}
	\item \textit{Remote control mode} allows attacker to take complete control of victim's device manually to perform delicate operation.
	\item \textit{Privacy extraction mode} captures and identify private data from the victim and send to the attacker.
\end{itemize}

\subsubsection{Hardware Specification}
The hardware we use is as follows and the relation between them is illustrated at Fig.~\ref{fig:hardware_specification}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by Raspberry Pi.
	\item\textit{Raspberry Pi} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
	\item\textit{Rubber Ducky} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
\end{itemize}
\begin{figure}[hbtp]
	\includegraphics[width=\linewidth]{./Figs/hardware_specification.png}
	\caption{Hardware Specification}
	\label{fig:hardware_specification}
\end{figure}
\subsubsection{Scripting Mode}
\tool under this mode works almost the same like the original Rubber Ducky with various improvement.

First \tool supports defense mechanism bypass. As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack. But such defense mechanism relies on visual notification to request authentication for unknown USB device. This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it automatically or manually. After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.

As the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of Rubber Ducky. Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation. This function enables attacks toward pure GUI programs and showed great potential in mobile attack scenario. Details can be obtained in Section~\ref{sec:experiment}.
\subsubsection{Remote Control Mode}
In \tool, we implement all components required to operate a computer/mobile remotely, including a video stream, keyboard/mouse emulation.

@@

This mode enable attacker to perform delicate operation that is beyond automation. Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by firewall running on the host machine.
\hongyi{I think this is a quite good selling point?}
\subsubsection{Privacy Extraction Mode}
\tool under this mode does not emulate other USB device and solely rely on the video stream function of USB 3.x.

@@

>>>>

As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension. In this section, we first introduce the hardware components we used to build \tool, then we focus on the three different attack modes we implement  for various scenario. The comparison of these modes is available at Table~\ref{table:mode_comparison}
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Mode & Detectibility & Automation & Power Consumption  \\
	\hline
	Scripting & Medium & Yes & Low\\
	\hline
	Remote Control & High & No & High \\
	\hline
	Privacy Extraction & Low & Yes & Medium\\
	\hline
	\end{tabular}
	\linebreak
	\caption{Comparison of Different Mode}
	\label{table:mode_comparison}
\end{table*}

\subsubsection{Hardware Specification}
The hardware we use is as follows and the relation between them is illustrated at Fig.~\ref{fig:hardware_specification}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by Raspberry Pi.
	\item\textit{Raspberry Pi} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
	\item\textit{Rubber Ducky} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
\end{itemize}
\begin{figure}[hbtp]
	\includegraphics[width=\linewidth]{./Figs/hardware_specification.png}
	\caption{Hardware Specification}
	\label{fig:hardware_specification}
\end{figure}
\textbf{Scripting Mode}
\tool under this mode works almost the same like the original Rubber Ducky with various improvement.

First \tool supports defense mechanism bypass. As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack. But such defense mechanism needs visual notification to request authentication for unknown USB device. This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it automatically or manually. After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.

As the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of Rubber Ducky. Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation. This function enables attacks toward pure GUI programs and showed great potential in mobile attack scenario. Details can be obtained in Section~\ref{sec:experiment}.

The advantage of this mode is that it archives defense bypass and attack feedback with low overhead. As mentioned above, we only require video stream at the begin(defense bypass) and the end(feedback) of the attack. Moreover, with mouse supported, \tool extends the original BadUSB attack surface and perform well in mobile device.

\textbf{Remote Control Mode}
In \tool, we implement all components required to operate a computer/mobile remotely, including a video stream, keyboard/mouse emulation.

@@

This mode enable attacker to perform delicate operation that is beyond automation. Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by firewall running on the host machine.
\hongyi{I think this is a quite good selling point?}

The advantage of this mode is that it can completely hijack the victim device. But this complete control also comes with the price of high power consumption and risk of being detected by the user.

\textbf{Privacy Extraction Mode}
\tool under this mode does not emulate other USB device and solely rely on the video stream function of USB 3.x.

@@

Though \tool under this mode is least detectable, \tool is also unable to fetch any information actively. All the video stream has to be analyzed and filtered to become usable private information.
